---
title: "Stardew Valley: Farm Planning"
author: "Nick D. Ungson"
output: rmarkdown::github_document
---

**Last updated:** `r Sys.time()`

All data below from the [Stardew Valley Wiki](https://stardewvalleywiki.com/Stardew_Valley_Wiki)

# Prep

Load data:
```{r eval = TRUE, echo = TRUE, message = FALSE, results = 'hide', warning = FALSE}
require(tidyverse)
require(here)

crops <- read.csv(
  here("crops.csv"), 
  header = TRUE, 
  stringsAsFactors = TRUE)
```

# Spring

What are all the crops available in [Spring](https://stardewvalleywiki.com/Spring)?

```{r}
crops %>% 
  filter(season == "spring") %>% 
  select(name:note2) %>% 
  print()
```


What are the most *profitable* (by gold per day) Spring crops?
```{r}
crops %>%
  filter(season == "spring") %>% 
  select(name, 
         gpd,
         buy, 
         type, 
         note1:note2) %>% 
  arrange(desc(gpd))
```

**Planning:** I want to plant the following in on the first day of Spring...

* 32 cauliflower
* 16 kale
* 16 potato
* 16 garlic
* 16 parsnip
* 32 green beans
* 8 blue jazz
* 8 tulip

**Cost Estimate**: How much money do I need on Spring 1 to buy all the seeds I want?

First, I wrote a function that will multiply the amount of seeds by the price of those seeds:
```{r}
PriceSeeds <- function(crop, n){
  price <- crops[crops$name == crop, "buy"]
  
  return(price * n)
}
```


Then, I passed each crop and # of seeds and summed them all:
```{r}
spring_money <- PriceSeeds("cauliflower", 32) + 
  PriceSeeds("green bean", 32) + 
  PriceSeeds("kale", 16) + 
  PriceSeeds("potato", 16) + 
  PriceSeeds("garlic", 16) + 
  PriceSeeds("parsnip", 16) + 
  PriceSeeds("blue jazz", 8) + 
  PriceSeeds("tulip", 8)
```

```{r}
print(paste("On Spring 1, you need $", spring_money, sep = ""))
```





# Summer

What are all the crops available in [Summer](https://stardewvalleywiki.com/Summer)?

```{r}
crops %>% 
  filter(season == "summer") %>% 
  select(name:note2) %>% 
  arrange(desc(type)) %>% 
  print()
```


What are the most *profitable* (by gold per day) summer crops?
```{r}
crops %>%
  filter(season == "summer") %>% 
  select(name, 
         gpd, 
         grow, regrow, max_harvest, 
         type) %>% 
  arrange(desc(gpd))
```