---
title: "Stardew Valley: Farm Planning"
author: "Nick D. Ungson"
output: rmarkdown::github_document
---

**Last updated:** `r Sys.time()`

# Prep

```{r eval = TRUE, echo = TRUE, message = FALSE, results = 'hide', warning = FALSE}
require(tidyverse)
require(here)

crops <- read.csv(
  here("crops.csv"), 
  header = TRUE, 
  stringsAsFactors = TRUE)

print(colnames(crops))

crops %>% 
  filter(season == "spring") %>% 
  select(name:note2) %>% 
  print()
```

# Spring

What are the most profitable (by *gold per day*) spring crops?

```{r}
crops %>%
  filter(season == "spring", 
         type == "fruit" | 
           type == "vegetable") %>% 
  select(name, 
         type, 
         buy, 
         gpd, 
         note1:note2) %>% 
  arrange(desc(gpd))
```

**Planning:** Going to try and plant the following in 2nd Spring...

* 32 cauliflower
* 16 kale
* 16 potato
* 16 garlic
* 16 parsnip
* 32 green beans
* 8 blue jazz
* 8 tulip

**Cost Estimate**: How much money do I need on Spring 1 to buy all the seeds I want?

First, I wrote a function that will multiply the amount of seeds by the price of those seeds:
```{r}
PriceSeeds <- function(crop, n){
  price <- crops[crops$name == crop, "buy"]
  
  return(price * n)
}
```


Then, I passed each crop and # of seeds and summed them all:
```{r}
spring_money <- PriceSeeds("cauliflower", 32) + 
  PriceSeeds("green bean", 32) + 
  PriceSeeds("kale", 16) + 
  PriceSeeds("potato", 16) + 
  PriceSeeds("garlic", 16) + 
  PriceSeeds("parsnip", 16) + 
  PriceSeeds("blue jazz", 8) + 
  PriceSeeds("tulip", 8)
```

```{r}
print(paste("On Spring 1, you need $", spring_money, sep = ""))
```



