---
title: "Stardew Valley: Farm Planning"
author: "Nick D. Ungson"
self_contained: false
output:
  html_document:
    highlight: haddock
    toc: true
    toc_depth: 2
    toc_float: 
      collapsed: false
      smooth_scroll: false
    df_print: paged
---

**Last updated:** `r Sys.time()`

All data below from the [Stardew Valley Wiki](https://stardewvalleywiki.com/Stardew_Valley_Wiki)

# prep

Load data:
```{r eval = TRUE, echo = TRUE, message = FALSE, results = 'hide', warning = FALSE}
require(tidyverse)
require(here)
require(DT)

#rmarkdown::github_document


crops <- read.csv(
  here("crops.csv"), 
  header = TRUE, 
  stringsAsFactors = TRUE)
```

Some functions:
**What crops are available in a season?**
```{r}
List <- function(season_name){
  crops %>% 
    filter(season == season_name) %>% 
    select(name, 
           type) %>% 
    arrange(desc(type)) %>% 
    return()
}
```

**What are the most profitable crops?** (measured in gold per day)
```{r}
GPD <- function(season_name){
  crops %>%
  filter(season == season_name) %>% 
  select(gpd, 
         name, 
         grow:regrow, 
         max_harvest) %>% 
  arrange(desc(gpd))
}
```

**Cost Estimate**: How much do *n* seeds of a crop cost?
```{r}
Price <- function(crop, n){
  price <- crops[crops$name == crop, "buy"]
  return(price * n)
}
```

# spring

What are all the crops available in [spring](https://stardewvalleywiki.com/spring)?

```{r}
List("spring")
```

Most valuable?
```{r}
GPD("spring")
```

## planning

I want to plant the following in on the first day of spring...

* 32 cauliflower
* 16 kale
* 16 potato
* 16 garlic
* 16 parsnip
* 32 green beans
* 8 blue jazz
* 8 tulip

Then, I passed each crop and # of seeds and summed them all:
```{r}
spring_cost <- Price("cauliflower", 32) + 
  Price("green bean", 32) + 
  Price("kale", 16) + 
  Price("potato", 16) + 
  Price("garlic", 16) + 
  Price("parsnip", 16) + 
  Price("blue jazz", 8) + 
  Price("tulip", 8)
```

```{r}
print(paste("On spring 1, you need $", spring_cost, sep = ""))
```

# summer

What are all the crops available in [summer](https://stardewvalleywiki.com/summer)?

```{r}
List("summer")
```

Most valuable?

```{r}
GPD("summer")
```

## planning
...


```{r}
summer_cost <- 
  Price("blueberry", 16) + 
  Price("red cabbage", 64) + 
  Price("melon", 46) + 
  Price("hops", 32) + 
  Price("hot pepper", 24) + 
  Price("tomato", 7) + 
  Price("radish", 7) + 
  Price("sunflower", 16) + 
  Price("wheat", 16) + 
  Price("corn", 16)
```

```{r}
print(paste("On summer 1, you need $", summer_cost, sep = ""))
```




# fall

What are all the crops available in [fall](https://stardewvalleywiki.com/fall)?

```{r}
List("fall")
```

```{r eval = FALSE}
datatable(crops, rownames = FALSE, 
          filter = "top", 
          options = list(pageLength = 20, 
                         scrollX = TRUE))
```

Most valuable?

```{r}
GPD("fall")
```

## planning
...

```{r}
fall_cost <- 
  Price("pumpkin", (32 * 3)) + 
  Price("artichoke", 64) + 
  Price("beet", 64) + 
  Price("cranberry", 64) + 
  Price("grape", 64) + 
  Price("amaranth", 16) + 
  Price("yam", 16) + 
  Price("eggplant", 16) + 
  Price("bok choy", 16)
```


```{r}
print(paste("On fall 1, you need $", fall_cost, sep = ""))
```


```{r}
fall_cost_all <- 
  Price("pumpkin", (32 * 3 * 2)) + 
  Price("artichoke", (64 * 3)) + 
  Price("beet", 64) + 
  Price("cranberry", 64) + 
  Price("grape", 64) + 
  Price("amaranth", (16 * 3)) + 
  Price("yam", (16 * 2)) + 
  Price("eggplant", 16) + 
  Price("bok choy", (16 * 6))

print(paste("On for entire fall, you need $", fall_cost_all, sep = ""))
```

